---
output:
  md_document:
    variant: markdown_github
---

# Purpose

Purpose of this work folder is for the Machine learning project

Ideally store a minimum working example data set in data folder.

Add binary files in bin, and closed R functions in code. Human Readable settings files (e.g. csv) should be placed in settings/


```{r}
install.packages(c("tidyverse", "tidytext", "caret", "text", "recipes", "tidymodels", "xgboost", "randomForest"))

install.packages("neuralnet")
rm(list = ls()) # Clean your environment:
gc() # garbage collection - It can be useful to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.


# Load the libraries
library(tidytext)
library(caret)
library(text)
library(recipes)
library(tidymodels)
library(xgboost)
library(randomForest)
library(tidyverse)
library(dplyr)

list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
import_multiple_csv()



temp <- list.files(path="data/.") #fetching the file names
for (i in 1:length(temp)) assign(gsub(pattern = ".csv",x=temp[i],replacement = ""), read.csv(paste("data/",temp[i],sep="")))#importing them into r
rm(i,temp)#removing temporary variables

n_distinct(actors$id)
#number of films variable

```

# Introduction 

Label outcome here and problem at hand. Make up fake scenario of why this machine learning bit needs to be done. 







# Data 


```{r}
head(actors)
head(countries)
head(crew)
head(genres)
head(languages)
head(movies)
#head(releases)
head(studios)
head(themes)
```

```{r}
(releases)  %>% filter(id == 1000001)


(movies) %>% filter(id == 1000001)
actors %>% filter(id == 1000001)
(countries)  %>% filter(id == 1000001)
(crew)  %>% filter(id == 1000001)
(genres)  %>% filter(id == 1000001)
(languages)  %>% filter(id == 1000001)
(studios)  %>% filter(id == 1000001)
(themes)  %>% filter(id == 1000001)

```



```{r}
library(dplyr)
library(tidyr)

# Aggregate actors this works
actors_agg <- actors %>%
  group_by(id) %>%
  summarise(actor_list = paste(name, collapse = ", "), .groups = 'drop')

# Aggregate countries this works 
countries_agg <- countries %>%
  group_by(id) %>%
  summarise(countries = paste(country, collapse = ", "), .groups = 'drop')

# Aggregate crew, works
crew_agg <- crew %>%
  group_by(id, role) %>%
  summarise(names = paste(name, collapse = ", "), .groups = 'drop') %>%
  pivot_wider(names_from = role, values_from = names, values_fill = list(names = ""))

#genre works
genres_agg <- genres %>%
  mutate(present = 1) %>%
  pivot_wider(names_from = genre, values_from = present, values_fill = list(present = 0))


#language works
languages_agg <- languages %>%
  mutate(present = 1) %>%
  pivot_wider(names_from = language, values_from = present, values_fill = list(present = 0)) %>% 
    select(-type)

studios_agg <- studios %>%
  group_by(id) %>%
  summarise(studio_list = paste(studio, collapse = ", "), .groups = 'drop')


themes_agg <- themes %>%
  group_by(id) %>%
  summarise(theme_list = paste(theme, collapse = ", "), .groups = 'drop')







releases_agg <- releases %>%
  mutate(present = 1) %>%
  pivot_wider(names_from = country, values_from = present, values_fill = list(present = 0))



# Merge all aggregated data frames with the movies data frame
final_data <- movies %>%
  left_join(actors_agg, by = "id") %>%
  left_join(countries_agg, by = "id") %>%
  left_join(crew_agg, by = "id") %>%
  left_join(genres_agg, by = "id") %>%
  left_join(languages_agg, by = "id") %>%
  left_join(studios_agg, by = "id") %>%
  left_join(themes_agg, by = "id")

# View the final data frame
head(final_data)

```























```{r clean movies}
#there are a number of films that do not have a rating attached to them, create a subset where they are removed


#many small films and not released films do not have a rating, small because need 30-50 reviews to get a rating.
movies_cleaned<-subset(movies, is.na(movies$rating)==FALSE) #now i have 85614 films, compared to 896400, except these have ratings. 

```

```{r experience}
#want to create a variable that counts how many films an actor/actress has been in
actors_experience <- actors %>%
  group_by(name) %>%
  summarise(experience = n_distinct(id)) #this counts how many films a person has been in
actors <- actors %>%
  left_join(actors_experience, by = "name") #join back to original data frame
remove(actors_experience)



#same thing but more complicated as both name and role have to be the same
crew_experience <- crew %>%
  group_by(name, role) %>%
  summarise(role_experience = n_distinct(id), .groups = 'drop')

crew <- crew %>%
  left_join(crew_experience, by = c("name", "role"))

```

